The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multi-Phase Forest Inventories

### 2017-09-21 rnw/Main structure and modules of the Package.Rnw
Still making errors...
update Andreas 21.09.2017(1)

Lets assume that the spatial distribution of a target variable (e.g. the timber volume) over the forest area is determined by a mathematical continuous function. The \textit{total} of the target variable $Y$ (e.g. the total timber volume of the forest) consequently is the integral of that function, in other words: the volume that expands under the surface of that function (Figure \ref{fig:inf_pop_apr}). We can thus reconsider our task of estimating e.g. the true timber volume of a forest as "estimating the integral of the unknown function that determines the timber volume distribution over our forest". From this perspective, the challenging part of an inventory is that the form of this function, and thus $Y$, is unknown. Theoretically, we still could get $Y$ by observing the function value $Y(x)$, called the \textit{local density}, at each possible point $x$ over the function plain (i.e. the forest area) and sum those obervations up. However, we see at the first spot that this is impossible, because the number of function values $Y(x)$ and thus the number of possible sample points $x$ is $infinite$. So the only thing we can do is to get a sample of $Y(x)$ to \textit{estimate} $Y$ by $\hat{Y}$. Since we thereby sample from an infinite population of sample points, and thus function values, this approach is consequently called the \textit{infinite population approach}. All estimators included in the \proglang{R} package \pkg{forestinventory} basically rest upon these theoretical thoughts. In practice, the value of $Y(x)$ is determined by measuring sample trees that lie within a circle (called sample plot) around the sample point $x$ located in the forest area, and aggregating their individual characteristics (e.g. their individual timber volumes). However, a key point to understand is that in the infinite population approach, a local density value $Y(x)$ has \textit{no spatial association}. Even if we use a spatial unit to calculate $Y(x)$, its value solely corresponds to the sample point $x$, which constitutes the sample unit. This has some obvious practical advantages over the finite population approach, where the sample units actually are cirular or rectangular plots. One is the impossibility of a perfect tesselation of an amorphous forest area by any kind of plot-shape, and hence, the population in the finite approach is, strictly speaking, not defined. The consideration of an underlying infinite population of sample points will also play an important role when incorporating auxiliary information in the frame of two- and three-phase estimation methods.

\begin{figure}[htb]
\centering
\resizebox{0.5\hsize}{!}{\includegraphics{fig/OnePhase.png}}
\caption{Visualization of the infinite population approach. The spatial distribution of the target variable $Y$ is determined by a continous function (green plain) from which 
only a sample of function values $Y(x)$ (dots on the plain) is known from a terrestrial survey.}
\label{fig:inf_pop_apr}
\end{figure}

@@

\subsection{Design-based vs. model-dependent approach}
\label{sec:db_vs_md}

>>>>

Most forest inventories gather the field information by randomly or systematically selecting points in the forest area defined by coordinates to which inventorists are sent. At these points, the inventorist measures sample trees that commonly lie within a circle (called sample plot) around the sample point $x$, and aggregates their individual characteristics (e.g. their individual timber volumes) to local plot densities (e.g. the timber density in $m^3/ha$). The estimators implemented in the \pkg{forestinventory} package use the so called \textit{infinite population approach} in order to bridge this sampling process to the mathematics behind the estimators. The infinite population approach assumes that the spatial distribution of the local density $Y(x)$ over the forest area is determined by a mathematical continuous function, as visualized in Figure \ref{fig:inf_pop_apr}. The \textit{population total} of the target variable (e.g. the total timber volume of the forest) is mathematically equivalent to the integral of that density function, which defines the volume under the green surface in Figure \ref{fig:inf_pop_apr}. From this perspective, the challenging part of an inventory is that the form of this function, and thus $Y$, is unknown. Theoretically, we still could get $Y$ by observing the function value,i.e. the local density $Y(x)$ at each possible point $x$ over the function plain (i.e. the forest area) and sum those obervations up. However, we see at the first spot that this is impossible, because the number of function values $Y(x)$ and thus the number of possible sample points $x$ is $infinite$. So we are left with only a sample of $Y(x)$ from an infinite population of sample points in order to \textit{estimate} $Y$ by $\hat{Y}$.

All estimators included in the \pkg{forestinventory} package basically rest upon this theoretical approach.

a key point for practical implementation is that in the infinite population approach, a local density value $Y(x)$ has \textit{no spatial association}. Even if we use a spatial unit to calculate $Y(x)$, its value solely corresponds to the sample point $x$, which constitutes the sample unit.

This has some obvious practical advantages over the finite population approach, where the sample units actually are cirular or rectangular plots. One is the impossibility of a perfect tesselation of an amorphous forest area by any kind of plot-shape, and hence, the population in the finite approach is, strictly speaking, not defined. The consideration of an underlying infinite population of sample points will also play an important role when incorporating auxiliary information in the frame of two- and three-phase estimation methods.

Furthermore, points can perfectly fill up any forest area with any amorphous shape, which is not possible if one were to use the \textit{finite population approach} where the sampling plot defined around the point is considered the sampling unit. The finite population approach has the disadvantage that circles don't tesselate perfectly and polygons will inevitably distort and pixelate the forest boundary.  In practice, the population of sampling units in the finite approach will almost never perfectly cover the forests. The consideration of an underlying infinite population of sample points will also play an important role when incorporating auxiliary information in the frame of two- and three-phase estimation methods.

%% Andi
Lets assume that the spatial distribution of a target variable (e.g. the timber volume) over the forest area is determined by a mathematical continuous function. The \textit{total} of the target variable $Y$ (e.g. the total timber volume of the forest) consequently is the integral of that function, in other words: the volume that expands under the surface of that function (Figure \ref{fig:inf_pop_apr}). We can thus reconsider our task of estimating e.g. the true timber volume of a forest as "estimating the integral of the unknown function that determines the timber volume distribution over our forest".

From this perspective, the challenging part of an inventory is that the form of this function, and thus $Y$, is unknown. Theoretically, we still could get $Y$ by observing the function value $Y(x)$, called the \textit{local density}, at each possible point $x$ over the function plain (i.e. the forest area) and sum those obervations up. However, we see at the first spot that this is impossible, because the number of function values $Y(x)$ and thus the number of possible sample points $x$ is $infinite$. So the only thing we can do is to get a sample of $Y(x)$ to \textit{estimate} $Y$ by $\hat{Y}$. Since we thereby sample from an infinite population of sample points, and thus function values, this approach is consequently called the \textit{infinite population approach}.

All estimators included in the \proglang{R} package \pkg{forestinventory} basically rest upon these theoretical thoughts. In practice, the value of $Y(x)$ is determined by measuring sample trees that lie within a circle (called sample plot) around the sample point $x$ located in the forest area, and aggregating their individual characteristics (e.g. their individual timber volumes). However, a key point to understand is that in the infinite population approach, a local density value $Y(x)$ has \textit{no spatial association}. Even if we use a spatial unit to calculate $Y(x)$, its value solely corresponds to the sample point $x$, which constitutes the sample unit. This has some obvious practical advantages over the finite population approach, where the sample units actually are cirular or rectangular plots. One is the impossibility of a perfect tesselation of an amorphous forest area by any kind of plot-shape, and hence, the population in the finite approach is, strictly speaking, not defined. The consideration of an underlying infinite population of sample points will also play an important role when incorporating auxiliary information in the frame of two- and three-phase estimation methods.

\begin{figure}[htb]
\centering
\resizebox{0.5\hsize}{!}{\includegraphics{fig/OnePhase.png}}
\caption{Visualization of the infinite population approach. The spatial distribution of a hypothetical density function for every point in a forested area is represented as wavy green surface.  Sample plots (grean circles) inform the inventorist of the value of the density function at that point.}
\label{fig:inf_pop_apr}
\end{figure}

@@

\subsection{Design-Based vs. Model-Dependent Approach}
\label{sec:db_vs_md}
